Design and Implementation of\\Anglican Probabilistic Programming Language

### 2016-09-02 slides/slides.tex
more slides

\begin{frame}{Anglican}
    A subset of Clojure, wrapped inside \texttt{defquery}:
    \begin{itemize}
        \item \texttt{if}, \texttt{when}, \texttt{cond},
            \texttt{case}, \texttt{let}, \texttt{and}, \texttt{or},
            \texttt{fn}. 
        \item Vector destructuring in bindings of \texttt{let} and \texttt{fn}.
        \item Compound literals for vectors, hash maps, and sets.
        \item \texttt{loop}/\texttt{recur} --- a convenience.
    \end{itemize}
    \bigskip
    Core library:
    \begin{itemize}
        \item All of Clojure core library, except for
            higher-order functions.
        \item  \texttt{map}, \texttt{reduce},
\texttt{filter}, \texttt{some}, \texttt{repeatedly},
\texttt{comp}, \texttt{partial}.
    \end{itemize}
    \bigskip
    Any Clojure function can be called from Anglican.
\end{frame}

>>>>

\begin{frame}{Design challenges and choices}
\begin{itemize}
    \item Anglican syntax: Clojure + probabilistic constructs.
		\begin{itemize}
			\item Subset of Clojure.
			\item Special forms \texttt{sample} and \texttt{observe}.
			\item Macros to delimit Anglican code within a Clojure program.
		\end{itemize}
		\pause
		\bigskip
    \item Source-to-source compilation of Anglican into Clojure.
		\begin{itemize}
			\item CPS Transformation, with some tricks.
			\item Transparent use of Clojure functions from Anglican.
		\end{itemize}
		\pause
		\bigskip
    \item Inference algorithms.
		\begin{itemize}
            \item Required to run an Anglican program.
			\item Step in at checkpoints (\texttt{sample} and \texttt{observe}).
			\item Execute programs by calling continuations repeatedly.
		\end{itemize}
\end{itemize}
\end{frame}

\begin{frame}{The language}
    A subset of Clojure, wrapped inside \texttt{defquery}:
    \begin{itemize}
        \item \texttt{if}, \texttt{when}, \texttt{cond},
            \texttt{case}, \texttt{let}, \texttt{and}, \texttt{or},
            \texttt{fn}. 
        \item Vector destructuring in bindings of \texttt{let} and \texttt{fn}.
        \item Compound literals for vectors, hash maps, and sets.
        \item \texttt{loop}/\texttt{recur} --- a convenience.
    \end{itemize}
    \bigskip
    Core library:
    \begin{itemize}
        \item All of Clojure core library, except for
            higher-order functions.
        \item  \texttt{map}, \texttt{reduce},
\texttt{filter}, \texttt{some}, \texttt{repeatedly},
\texttt{comp}, \texttt{partial}.
    \end{itemize}
    \bigskip
    Any Clojure function can be called from Anglican.
\end{frame}
